%-------------------------
% Resume in Latex
% Integrated from portfolio and existing resume content
%------------------------

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage[most]{tcolorbox}

\setlength{\multicolsep}{0pt}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}

\tcbset{
	frame code={},
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\urlstyle{same}
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}}
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.2mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{1mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

\newcommand{\name}{Nidumolu Bala Rohith}
\newcommand{\phone}{7386432810}
\newcommand{\emaila}{rohithnidumolu@gmail.com}
\newcommand{\location}{Vuyyuru, Andhra Pradesh}
\newcommand{\linkedin}{linkedin.com/in/rohithnidumolu}
\newcommand{\github}{github.com/Rohith-180503}
\newcommand{\portfolio}{rohith-180503.github.io/PORTFOLIO}

\begin{document}
\fontfamily{cmr}\selectfont

\begin{center}
{\Huge \textbf{\name}} \\[3pt]
\small
\location \textbar\ +91-\phone \textbar\ \href{mailto:\emaila}{\emaila} \\
\href{https://\linkedin}{\faLinkedin\ \linkedin} \hspace{2mm}
\href{https://\github}{\faGithub\ \github} \hspace{2mm}
\href{https://\portfolio}{\faGlobe\ \portfolio}
\end{center}

\cvsection{Professional Summary}
\begin{justify}\small
Full-stack developer specializing in building scalable, high-performance web applications. Expertly navigating the MERN stack alongside Java and modern database architectures (PostgreSQL, MongoDB, SQLite) to deliver secure, end-to-end engineering solutions that bridge complex backend logic with premium, interactive user experiences. Seeking software engineering roles to apply robust problem-solving skills and expertise in responsive UI engineering.
\end{justify}
\vspace{-2mm}

\section{\textbf{Education}}
\resumeSubHeadingListStart
  \resumeSubheading
    {SRKR Engineering College}{CGPA: 7.95/10}
    {B.Tech in Electrical and Electronics Engineering}{2020 -- 2024}
    \resumeItemListStart
      \item \textbf{Final Year Project:} EV Regenerative Braking Simulation -- Modeled battery-motor dynamics and motor torque behavior using MATLAB and Simulink to analyze energy recovery efficiency and system stability.
    \resumeItemListEnd
  \resumeSubheading
    {Narayana Junior College, Vijayawada}{Score: 910/1000}
    {Intermediate (MPC)}{2018 -- 2020}
  \resumeSubheading
    {Flora English Medium School, Vuyyuru}{GPA: 10/10}
    {Secondary School}{2017 -- 2018}
\resumeSubHeadingListEnd
\vspace{-4.5mm}

\section{\textbf{Experience}}
\resumeSubHeadingListStart
  \resumeSubheading
    {Voltech Engineers Pvt. Ltd.}{Chennai, India}
    {Graduate Engineer Intern}{Jul 2024 -- Mar 2025}
    \vspace{-1.8mm}
    \resumeItemListStart
      \item Supported high-voltage substation commissioning activities through technical checks, documentation, and team coordination.
      \item Prepared single-line diagrams and control panel layout documents with attention to accuracy and engineering standards.
      \item Assisted with testing, issue identification, and troubleshooting during site and system-level activities.
      \item Maintained technical records and process documentation to support project execution and compliance.
    \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-6.5mm}

\section{\textbf{Projects}}
\resumeSubHeadingListStart

  \resumeProject
    {LearnHub - Full-Stack LMS}
    {Professional education platform featuring secure JWT authentication and Stripe payment infrastructure}
    {Node.js, Express, SQLite, React 19, JWT, Stripe}
    {\href{https://github.com/Rohith-180503/ONLINE-LEARNING-WEBSITE}{GitHub}}
    \resumeItemListStart
      \item Engineered a complete transition from a static UI to a dynamic, production-ready platform with decoupled architecture.
      \item Implemented secure JWT cookie-based session management and course progress persistence across devices.
      \item Integrated Stripe Checkout and webhooks for automated enrollment and commercial-ready payment processing.
      \item Optimized state management using React Context API for real-time guest-to-user cart synchronization.
    \resumeItemListEnd
    \vspace{-2mm}

  \resumeProject
    {TaskFlow Productivity Manager}
    {Sophisticated task management application focused on state persistence and accessible user workflows}
    {Vanilla JS, LocalStorage, DOMPurify, CSS3}
    {\href{https://github.com/Rohith-180503/TODO-LIST-APP}{GitHub}}
    \resumeItemListStart
      \item Developed complex filtering and sorting algorithms alongside CRUD functionality for real-time task management.
      \item Implemented a robust 'Undo' system using custom toast notifications and reliable LocalStorage persistence.
      \item Prioritized security with DOMPurify sanitization and ensured full ARIA accessibility for screen reader compliance.
      \item Designed a responsive UI with inline editing, priority-based organization, and theme persistence.
    \resumeItemListEnd
    \vspace{-2mm}

  \resumeProject
    {Dragon Dash Arcade}
    {Immersive browser-based arcade game utilizing high-performance animation and custom physics logic}
    {JavaScript, HTML Canvas, CSS Animations}
    {}
    \resumeItemListStart
      \item Created a seamless gameplay loop using \texttt{requestAnimationFrame} for high-performance animation synchronization.
      \item Implemented advanced collision detection algorithms, dynamic obstacle generation, and keyboard interaction logic.
      \item Engineered a low-latency interactive experience with progressive difficulty and real-time score tracking.
    \resumeItemListEnd
    \vspace{-2mm}

  \resumeProject
    {Netflix India Clone}
    {High-fidelity landing page clone prioritizing pixel-perfect design and cinematic user engagement}
    {HTML5, CSS3, Flexbox, CSS Grid}
    {\href{https://github.com/Rohith-180503/NETFLIX-CLONE}{GitHub}}
    \resumeItemListStart
      \item Leveraged advanced CSS Grid and Flexbox for precise layout control and high-fidelity brand replication.
      \item Integrated autoplaying video mockups and semi-transparent overlays for an immersive visual experience.
      \item Developed interactive FAQ components with smooth state transitions and full mobile responsiveness.
    \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-5.5mm}

\section{\textbf{Technical Skills and Interests}}
\begin{itemize}[leftmargin=0.05in, label={}]
  \small{\item{
    \textbf{Languages}{: Java, JavaScript, Node.js, SQL, HTML5, CSS3} \\
    \textbf{Developer Tools}{: Git, GitHub, VS Code, Vite, Postman, Microsoft Office} \\
    \textbf{Frameworks/Lib}{: React.js, Express.js, Bootstrap, JWT, Stripe API, Context API, DOMPurify} \\
    \textbf{Databases}{: MongoDB, PostgreSQL, SQLite, LocalStorage, REST API fundamentals} \\
    \textbf{Soft Skills}{: Communication, analytical troubleshooting, teamwork, adaptability, technical documentation} \\
    \textbf{Coursework}{: Data Structures, DBMS, Web Development, OOP, Systems Engineering} \\
    \textbf{Areas of Interest}{: Full-Stack Development, Responsive UI Engineering, Secure Backend Architecture}
  }}
\end{itemize}
\vspace{-14pt}

\section{\textbf{Portfolio Highlights}}
\vspace{-0.4mm}
\resumeSubHeadingListStart
  \resumePOR{Frontend Development, }{responsive layouts, reusable components, interactive UI flows}{Portfolio focus}
  \resumePOR{Professional Strengths, }{debugging, maintainable code structure, practical implementation}{Core profile}
  \resumePOR{Links, }{\href{https://\github}{GitHub} \textbar\ \href{https://\portfolio}{Portfolio} \textbar\ \href{https://\linkedin}{LinkedIn}}{Online presence}
\resumeSubHeadingListEnd
\vspace{-5mm}

\section{\textbf{Additional Information}}
\vspace{-0.4mm}
\resumeSubHeadingListStart
  \resumePOR{Languages, }{English, Hindi, Telugu}{}
\resumeSubHeadingListEnd
\vspace{-4mm}
\setlength{\footskip}{4.08003pt}

\end{document}
